Spitzer, Gaia and the Potential of the Milky Way

### 2013-07-27 text/paper1/paper.tex
starting to write discsussion

@@

Many orbit fitting methods for measuring the Galactic potential assume that the stars in a given stream are on the same
orbit. \cite{binney??} show that this assumption leads to biased
potential parameters, even without realistic observational errors on
the kinematic data. The method presented above is
free of this assumption and instead \emph{relies} on the fact that
each star is on a different orbit and is thus an independent potentiometer. The power of this method is in
the joint constraint that the best potential is the one that gets the
most of these individual orbits to intersect the progenitor
over the history of interaction with the system.

[merge these paragraphs (above, below)]

The great strength of the  JZSH ({\it can we come up with a catchy name?}) method is its simplicity:
it requires only the assumption a satellite mass $m_{\rm sat}$ and  backwards integration of orbits.
There are no assumptions made about or N-body modeling required to follow the internal distribution of satellite stars or accurately assess the degree of alignment of
debris with a single orbit.
In fact, the method relies on the ability to measure {\it differences} in orbital properties --- these differences result in different orbital time periods for the debris and the
satellite which leads to their paths intersecting during the backwards integration.

There are two other apparent strengths of the method which require further investigation.
First it appears applicable to any debris that is known to come from a single object, and not restricted only to the very coldest tidal streams. For example, in principle the
method could  applied to the vast debris {\it clouds} that have been discovered subtending hundreds-thousands square degrees \citep[e.g. the Triangulum Andromeda
and Hercules-Aquila clouds]{rochapinto04,belokurov06}, or even stars that have only associations in orbital properties and do not form a coherent spatial structure
\citep[such as the angular momentum groupings in local giants found by][]{helmi99}.
Second, it appears trivial to combine constraints from multiple debris systems at once by simply integrating all debris from several satellites simultaneously with $D_{\rm
ps}$ defined appropriately for each star separately.

>>>>

Many orbit fitting methods for measuring the Galactic potential assume that the stars in a given stream are on the same
orbit. \cite{binney??} show that this assumption leads to XXX\% biases in the 
potential parameters, even without realistic observational errors on
the kinematic data. The \emph{Rewinder} is
free of this assumption and instead \emph{relies} on the fact that
each star is on a different orbit, and is thus an independent potentiometer: the best potential is the one that gets the
most of these orbits to intersect the progenitor
over the history of interaction with the system. The strength of this method is in the simplicity: it requires only a rough estimate of the satellite mass $m_{\rm sat}$ combined with backwards integration of orbits. There are no assumptions made about, or N-body modeling of, the internal distribution of satellite stars.

[TODO: this paragraph needs work]
There are two other apparent strengths of the method which require further investigation.
First it appears applicable to any debris that is known to come from a single object, and not restricted only to the very coldest tidal streams. For example, in principle the
method could  applied to the vast debris {\it clouds} that have been discovered subtending hundreds-thousands square degrees \citep[e.g. the Triangulum Andromeda
and Hercules-Aquila clouds]{rochapinto04,belokurov06}, or even stars that have only associations in orbital properties and do not form a coherent spatial structure
\citep[such as the angular momentum groupings in local giants found by][]{helmi99}.
Second, it appears trivial to combine constraints from multiple debris systems at once by simply integrating all debris from several satellites simultaneously with $D_{\rm
ps}$ defined appropriately for each star separately.

@@
